Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-02-12 Multiresolution_framework/ltx/manuscript.tex
minor correction

The $m^{th}$  order cardinal B-spline function is defined by the recurrence relation \citep{Chui1992} 
\begin{equation}
N_{m}\left(r\right) = \left(N_{m-1}\ast N_{1}\right)\left(r\right) = \int_0^{1} N_{m-1}\left( r-r'\right)\,\mathrm{d}r',
\label{SplineConvolutionIntegral}
\end{equation}
where $m>1$, $\ast$ denotes convolution, and $N_1\left(r\right)$ is the characteristic function of the unit interval $\left[ 0,1\right)$, also known as indicator function, i.e.
\begin{equation}
N_{1}\left(r\right)=
\begin{cases}
1 & \text{if $ 0\le r<1$}, \\
0 & \mathrm{elsewhere}.
\end{cases}
\end{equation}
Following this, a B-spline of any order, $N_m(r)$, can be computed using the recursive expression defined by \citet{DeBoor2001}
\begin{equation}\label{eq:MRA-DoBoorFormula}
 N_{m}\left(r\right)=\frac{r}{m-1}N_{m-1}\left(r\right)+\frac{m-r}{m-1}N_{m-1}\left(r-1\right) \quad m>1.
 \end{equation}
The most commonly used form of splines is the cubic spline $\left(m=4\right)$, comprised of third degree polynomials added together at the joining points, with an explicit expression given by
\begin{align}
3!N_{4}\left(r\right)=
\begin{cases}
r^3 & \text{if $ 0\le r\le1$}, \\
4-12r+12r^2-3r^3 & \text{if $1\le r\le2$}, \\
-44+60r-24r^2+3r^3 & \text{if $2\le r\le3$}, \\
64-48r+12r^2-r^3 & \text{if $3\le r\le4$}, \\
0 & \mathrm{elsewhere}.
\end{cases}
\end{align}
One important feature of the B-spline functions is the \emph{partition of unity} property, meaning that the unity can be expressed as a linear sum of B-splines, i.e
\begin{equation}
	\sum_{l}N_m(r+l)\equiv1.
	\end{equation}
This is important as the underlying field can be reconstructed when its saturated without introducing numerical errors which is not the case for example when Gaussian basis functions are used.

@@

In order to analytically calculate elements of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Gamma$, the scaling and wavelet basis functions must be expanded in terms of $N_m$ at the appropriate scale using the two-scale relation pair defined in equations (\ref{eq:MRA-TwoScalepair1}-\ref{eq:MRA-TwoScalepair2coefs}). For scaling functions this can be done  by using Eq.~\eqref{eq:MRA-TwoScalepair1} recursively, giving

@@

\mathcal F(N_m(r))=\left(\frac{1-\mathrm{exp}(-2\pi i \nu)}{2\pi i\nu}\right)^m.

@@

	&=\sum_{n=0}^{3m-2} \left[\mathbf q\right]_n \mathrm{exp}(-2\pi in\nu)\left(\frac{1-\mathrm{exp}(-\pi i \nu)}{\pi i\nu}\right)^m.\label{eq:MRA-Wavelettransform}

>>>>

The $m^{th}$  order cardinal B-spline function is defined by the recurrence relation \citep{Chui1992} 
\begin{equation}
N_{m}\left(r\right) = \left(N_{m-1}\ast N_{1}\right)\left(r\right) = \int_0^{1} N_{m-1}\left( r-r'\right)\,\mathrm{d}r',
\label{SplineConvolutionIntegral}
\end{equation}
where $m>1$, $\ast$ denotes convolution, and $N_1\left(r\right)$ is the characteristic function of the unit interval $\left[ 0,1\right)$, also known as indicator function, i.e.
\begin{equation}
N_{1}\left(r\right)=
\begin{cases}
1 & \text{if $ 0\le r<1$}, \\
0 & \mathrm{elsewhere}.
\end{cases}
\end{equation}
Following this, a B-spline of any order, $N_m(r)$, can be computed using the recursive expression defined by \citet{DeBoor2001}
\begin{equation}\label{eq:MRA-DoBoorFormula}
 N_{m}\left(r\right)=\frac{r}{m-1}N_{m-1}\left(r\right)+\frac{m-r}{m-1}N_{m-1}\left(r-1\right) \quad m>1.
 \end{equation}
The most commonly used form of splines is the cubic spline $\left(m=4\right)$, comprised of third degree polynomials added together at the joining points, with an explicit expression given by
\begin{align}
3!N_{4}\left(r\right)=
\begin{cases}
r^3 & \text{if $ 0\le r\le1$}, \\
4-12r+12r^2-3r^3 & \text{if $1\le r\le2$}, \\
-44+60r-24r^2+3r^3 & \text{if $2\le r\le3$}, \\
64-48r+12r^2-r^3 & \text{if $3\le r\le4$}, \\
0 & \mathrm{elsewhere}.
\end{cases}
\end{align}
One important feature of the B-spline functions is the \emph{partition of unity} property, meaning that the unity can be expressed as a linear sum of B-splines, i.e
\begin{equation}
	\sum_{l}N_m(r+l)\equiv1.
	\end{equation}
This is important as the underlying field can be reconstructed when it is saturated without introducing numerical errors which is not the case for example when Gaussian basis functions are used.

@@

In order to analytically calculate elements of $\boldsymbol\Lambda_{x}$ and $\boldsymbol\Gamma$, the scaling and wavelet basis functions must be expanded in terms of $N_m$ at the appropriate scale using the two-scale relation pair defined in Eqs.~(\eqref{eq:MRA-TwoScalepair1}-\eqref{eq:MRA-TwoScalepair2coefs}). For scaling functions this can be done  by using Eq.~\eqref{eq:MRA-TwoScalepair1} recursively, giving

@@

\mathcal F(N_m(r))=\left(\frac{1-\mathrm{exp}(-2\pi i \nu)}{2\pi i\nu}\right)^{m}.

@@

	&=\frac{1}{2}\sum_{n=0}^{3m-2} \left[\mathbf q\right]_n \mathrm{exp}(-\pi in\nu)\left(\frac{1-\mathrm{exp}(-\pi i \nu)}{\pi i\nu}\right)^m.\label{eq:MRA-Wavelettransform}
